---
title: "Quickstart"
author:
- "Kim Seonghyun"
date: "`r Sys.Date()`"
output: 
  html_document:
      toc: true
      toc_float: true
      theme: flatly
vignette: >
  %\VignetteIndexEntry{quickstart}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
library(cbar, warn.conflicts = F)
library(dplyr, warn.conflicts = F)
library(ggplot2, warn.conflicts = F)
```

### Installation

Either you try stable CRAN version

```{r, eval = F}
install.packages("cbar")
```

Or unstable development version

```{r, eval = F}
devtools::install_github("zedoul/cbar")
```

You'll need to use `library` to load as follows:

```{r, eval = F}
library(cbar)
```

### Introduction

`cbar` is an R package for detecting anomaly in time-series data with Bayesian inference.
Although there are many packages to detect anomaly in the world, relatively few packages
provide functions for visually and/or analytically abstracting the output.

The `cbar` package aims to provide simple-to-use functions for detecting anomaly, and abstracting the analysis output.

### Detecting anomaly

A minimal example would be like:

```{r}
library(cbar)

.data <- mtcars
rownames(.data) <- NULL
datetime <- seq(from = Sys.time(), length.out = nrow(.data), by = "mins")
.data <- cbind(datetime = datetime, .data)

ref_session <- 1:16
mea_session <- 17:nrow(.data)

.cbar <- cbar(.data, ref_session, mea_session)
plot_ts(.cbar)
```

You may wonder why it uses `reference` and `measurement` instead of `training` and `testing`. In anomaly detection, espeically in telecommuncation field, `performance reference period` 
refers a period which serves a basis for defining anomaly, and `performance measurement period` refers the period during which performance parameters are measured.

If you hope to see the abstracted outcome, then:

```{r}
summarise_session(.cbar)
```

or you can just use `print` function as follows:

```{r}
print(.cbar)
```

If you hope to see details of those anomalies:

```{r}
summarise_anomaly(.cbar, .session = "measurement")
```